\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
correct the \center L801 703(?)

\begin{abstract} 
\KCnote{ \blue{......numerical modelling of multiphase flow in porous media has a wide range of applications in science and engineering. Viscous fingering, a fluid instability can be a major concern regarding enhanced oil-recovery methods (EOR). Continuity equation and the Darcy's law govern the processes, while pressure, velocity, saturation and permeability are quantities that define the behaviour of the flow. A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model. The current model is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to increase the computational accuracy of numerical methods used in geophysical fluid mechanics and tackle the difficulties that commercial resevoir simulators may rise when using low order finite volume/differences methods based on structured grids. The governing multiphase porous media flow equations are solved using an adaptive and unstructured mesh. The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
%Moreover, the mesh adaptivity algorithm employs multi-constraints on element size in different regions of the porous medium to resolve multi-scale transport phenomena. The scheme captures the key characteristics of the flow while its applicable to heterogeneous porous media and geological formations. We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.
In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion. Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution...}}

@@

%\begin{figure}
%\centering
%\subfigure[flow at t=1000  (adaptive coarse mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_coarse_vel_magn.pdf}}\\[2mm]%
%\subfigure[flow at t=1000  (adaptive and fine mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_vel_magn.pdf}}\\[2mm]%
%\subfigure[flow at t=1000  (adaptive and refined mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_refine_vel_mag.pdf}}%
%\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions. From top to bottom These graphs describe the velocity magnitude for single inlet with adaptive and fine mesh (a) and adaptive and refined mesh (b). The main difference between the (a) and (b) lies in the first part and how the velocity magnitude is builded up as a relation of phase $1$ volume fraction.}
%\label{fig:vel_magn1}
%\end{figure}

>>>>

\begin{abstract} 
\KCnote{ \blue{ Multiphase flows in porous media is an interesting and important subject in fields ranging from oil recovery to medicine. From physics standpoint, the complex structures observed in multiphase flows, also know as fingers, are especially interesting. Much work both experimental and numerical has been done on invasion systems where one fluid is injected into a system filled with another fluid. These patterns are causing an instability known as Safmman-Taylor or Viscous fingering. Continuity equation and the Darcy's law govern the processes, while pressure, velocity, saturation and permeability are quantities that define the behaviour of the flow. A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model. The current model is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to increase the computational accuracy of numerical methods used in geophysical fluid mechanics and tackle the difficulties that commercial resevoir simulators may rise when using low order finite volume/differences methods based on structured grids. The governing multiphase porous media flow equations are solved using an adaptive and unstructured mesh. The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
%Moreover, the mesh adaptivity algorithm employs multi-constraints on element size in different regions of the porous medium to resolve multi-scale transport phenomena. The scheme captures the key characteristics of the flow while its applicable to heterogeneous porous media and geological formations. We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.
In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion. Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution...}}

@@
